Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Update paper.qmd
Added in-text citations for appendix.

## Target Population and Sampling Frame
The poll targets registered voters in the United States, with a particular focus on voters in swing states for presidential races. Consequently, the target population is registered voters of the United States of America and the sampling frame is the voter file, a national list of registered voters from which NYC employs random sampling to create their pollsters. This voter file contains information on more than 200 million Americans that includes information about their party affiliation, voting history, and  basic demographic information. From this sampling frame, respondents are randomly selected while balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population.

## Recruitment Methods
The poll relies on random digit dialing to reach voters, predominantly via cell phones. While landlines are also called, the dominance of cellphone usage aligns with contemporary communication trends. This results in their rendition of random sampling, which contributes to the external validity of data. However, reaching voters by phone has become more difficult due to low response rates requiring many attempts to secure responses from certain individuals (response rates are as  low as 2% at NYC). In fact, according to an article by Emerson College, telephone polling has become entirely obsolete (@EmersonCollege). Despite this, the phone methodology is still seen as effective for its ability to quickly reach a diverse voter pool across various states as well as seen as the golden standard for polling. Although this can be seen as random sampling, the concern of low response rates and reliance on dialing to reach voters raises concerns of selection bias. There are questions as to whether a certain demographic will be more responsive to being reached through a cell phone. Moreover, voters that are reached over the phone may feel the urge to provide more ‘socially desirable’ responses that are not reflective of their true opinions.

## Non-Response Remedies
With a response rate of 2%, there is valid concern over non-response bias underrepresenting certain demographics. The poll addresses non-response through a combination of front-end sampling adjustments (calling harder-to-reach voters) and post-survey weighting. Weighting is applied to ensure that the final sample aligns with the demographic and political composition of the electorate, based on voter file data. Non-response bias is a persistent challenge, and even though weighting helps, it's impossible to be certain that respondents are fully representative of those who do not respond. Experiments with alternative methods, such as mail surveys with incentives of cash vouchers have shown to increase response rate up to 30% (New York Times).

@@

If the methodology randomly sampled from the target population without regard for the distribution of demographics in the state, significant increases to the sample sizes have to be made. Random sampling will have largely less precision in representing the distribution of different demographics within a given state unless a large enough sample size were to be drawn. Although it is ideal to have probability based sampling increasingly resemble the demographic distribution quota with growing sample sizes, it is unfeasible to conduct such a large scale poll as this approach would encounter a limitation of resources. With declining response rates and the difficulty of reaching voters, New York Times/Siena's nonprobability sampling is a more realistic and efficient method of polling than probability sampling is (@tellingstorieswithdata). As such, the stratified sampling approach allows New York Times/Siena to represent the entire target population with a sample size of 1,000.

@@

The Times/Siena Poll’s approach to questionnaire design reflects a careful effort to craft unbiased, relevant, and inclusive questions. By tailoring questions to current events and topics of widespread interest, the poll aims to capture public sentiment on issues that directly affect voters' attitudes, such as economic conditions or recent political debates. This responsiveness to current events strengthens the poll's relevance and allows it to track shifts in opinion over time. The poll’s commitment to neutrality is a significant strength. Each question is designed to ensure that respondents, regardless of their political views, feel that their perspectives are fairly represented. The team behind the poll spends substantial time crafting response options to reflect a balanced spectrum of views, minimizing potential response bias and enhancing the questionnaire's reliability across different demographic and ideological groups (@NewYorkTimes). Clarity is also a central focus in their questionnaire development. The team emphasizes ensuring that each question is clear and unambiguous, minimizing the risk of misinterpretation. This dedication to straightforward, widely understandable questions improves the validity of responses, as it reduces the chance that respondents interpret questions differently based on background or knowledge level.

@@

Despite the strengths of the Times/Siena Poll’s questionnaire design, there are some limitations. One notable concern is that, although the poll tries to avoid leading questions, any standardized questionnaire may still unintentionally prime respondents or introduce subtle biases, especially when questions involve sensitive or polarizing topics. Although the pollster tries to avoid attrition bias by keeping each interview less than 15 minutes, in seeking to make questions clear and concise, the questionnaire may not capture the full nuance of voter opinions, especially on multifaceted issues like economic policy or social justice. While the poll strives to capture real views without introducing new ideas, respondents are still prone to a social desirability bias. This is especially possible in phone interviews, where respondents may be more inclined to provide answers they perceive as socially acceptable rather than expressing their true opinions. Although the design aims to be fair, the influence of an interviewer’s presence may subtly affect responses (@thepsygologyofsurveyresponse)

@@

According to 2024 polling data conducted by New York Times, the swing states are determined to be the following:

@@

## Party Affiliation
Which party do you prefer a candidate to be chosen from?
Democratic Party's candidate
Republican Party's candidate
Another Party's candidate
In the 2020 presidential election, who did you vote for?  If you did not vote, who would you have voted for?
Donald Trump
Joe Biden
Neither
Other…
If planning to vote, which presidential candidate are you planning to vote for?
If you are abstaining, please select which candidate you feel more strongly about.
Donald Trump
Kamala Harris
Other...
\newpage

>>>>

## Target Population and Sampling Frame
The poll targets registered voters in the United States, with a particular focus on voters in swing states for presidential races. Consequently, the target population is registered voters of the United States of America and the sampling frame is the voter file, a national list of registered voters from which NYC employs random sampling to create their pollsters @nyt_poll. This voter file contains information on more than 200 million Americans that includes information about their party affiliation, voting history, and  basic demographic information. From this sampling frame, respondents are randomly selected while balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population @nyt_poll.

## Recruitment Methods
The poll relies on random digit dialing to reach voters, predominantly via cell phones. While landlines are also called, the dominance of cellphone usage aligns with contemporary communication trends. This results in their rendition of random sampling, which contributes to the external validity of data. However, reaching voters by phone has become more difficult due to low response rates requiring many attempts to secure responses from certain individuals (response rates are as  low as 2% at NYC). In fact, according to an article by Emerson College, telephone polling has become entirely obsolete @kimball_polling. Despite this, the phone methodology is still seen as effective for its ability to quickly reach a diverse voter pool across various states as well as seen as the golden standard for polling. Although this can be seen as random sampling, the concern of low response rates and reliance on dialing to reach voters raises concerns of selection bias. There are questions as to whether a certain demographic will be more responsive to being reached through a cell phone. Moreover, voters that are reached over the phone may feel the urge to provide more ‘socially desirable’ responses that are not reflective of their true opinions.

## Non-Response Remedies
With a response rate of 2%, there is valid concern over non-response bias underrepresenting certain demographics. The poll addresses non-response through a combination of front-end sampling adjustments (calling harder-to-reach voters) and post-survey weighting. Weighting is applied to ensure that the final sample aligns with the demographic and political composition of the electorate, based on voter file data. Non-response bias is a persistent challenge, and even though weighting helps, it's impossible to be certain that respondents are fully representative of those who do not respond. Experiments with alternative methods, such as mail surveys with incentives of cash vouchers have shown to increase response rate up to 30% @nyt_poll.

@@

If the methodology randomly sampled from the target population without regard for the distribution of demographics in the state, significant increases to the sample sizes have to be made. Random sampling will have largely less precision in representing the distribution of different demographics within a given state unless a large enough sample size were to be drawn. Although it is ideal to have probability based sampling increasingly resemble the demographic distribution quota with growing sample sizes, it is unfeasible to conduct such a large scale poll as this approach would encounter a limitation of resources. With declining response rates and the difficulty of reaching voters, New York Times/Siena's nonprobability sampling is a more realistic and efficient method of polling than probability sampling is @tellingstories. As such, the stratified sampling approach allows New York Times/Siena to represent the entire target population with a sample size of 1,000.

@@

The Times/Siena Poll’s approach to questionnaire design reflects a careful effort to craft unbiased, relevant, and inclusive questions. By tailoring questions to current events and topics of widespread interest, the poll aims to capture public sentiment on issues that directly affect voters' attitudes, such as economic conditions or recent political debates. This responsiveness to current events strengthens the poll's relevance and allows it to track shifts in opinion over time. The poll’s commitment to neutrality is a significant strength. Each question is designed to ensure that respondents, regardless of their political views, feel that their perspectives are fairly represented. The team behind the poll spends substantial time crafting response options to reflect a balanced spectrum of views, minimizing potential response bias and enhancing the questionnaire's reliability across different demographic and ideological groups @nyt_poll. Clarity is also a central focus in their questionnaire development. The team emphasizes ensuring that each question is clear and unambiguous, minimizing the risk of misinterpretation. This dedication to straightforward, widely understandable questions improves the validity of responses, as it reduces the chance that respondents interpret questions differently based on background or knowledge level.

@@

Despite the strengths of the Times/Siena Poll’s questionnaire design, there are some limitations. One notable concern is that, although the poll tries to avoid leading questions, any standardized questionnaire may still unintentionally prime respondents or introduce subtle biases, especially when questions involve sensitive or polarizing topics. Although the pollster tries to avoid attrition bias by keeping each interview less than 15 minutes, in seeking to make questions clear and concise, the questionnaire may not capture the full nuance of voter opinions, especially on multifaceted issues like economic policy or social justice. While the poll strives to capture real views without introducing new ideas, respondents are still prone to a social desirability bias. This is especially possible in phone interviews, where respondents may be more inclined to provide answers they perceive as socially acceptable rather than expressing their true opinions. Although the design aims to be fair, the influence of an interviewer’s presence may subtly affect responses @psychology_survey_response.

@@

According to 2024 polling data conducted by New York Times, the swing states are determined to be the following @boyce_swing_states:

@@

## Party Affiliation
Which party do you prefer a candidate to be chosen from?
Democratic Party's candidate
Republican Party's candidate
Another Party's candidate
In the 2020 presidential election, who did you vote for?  If you did not vote, who would you have voted for?
Donald Trump
Joe Biden
Neither
Other…
If planning to vote, which presidential candidate are you planning to vote for?
If you are abstaining, please select which candidate you feel more strongly about.
Donald Trump
Kamala Harris
Other...
